Supplemental material for: Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-11-24 Scripts/Supplements.Rmd
Included Figure S10 top

>>>>

```{r toeFigureS10, eval = T,  echo = F, fig.width=7, fig.height=5, fig.cap = "Changes in the stock share proportion of top 5 most valuable stocks by 2030 (2021-2040) relative to 1951-2005. Lines represent the average change in transboundary stock share ratio (Methods) with arrows going from EEZ with decreasing stock share (point) to those gaining shares (arrowhead).}

img <- readPNG("../Figures/FigS10.png")
grid.raster(img)
